### 2022-05-16 supplement.Rmd
Add footnotes

```{r, r_assumed}
# Compute empirical estimate of the correlation between dependent samples
dat_meta %>%
  mutate(
    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
    d_diff = case_when(
      !is.na(d) ~ d,
      !is.na(d_z_t) ~ d_z_t,
      !is.na(d_z_f) ~ d_z_f,
      !is.na(d_z_diff) ~ d_z_diff
    ),
    # Compute empirical correlation
    # Based on the SD of the difference and the SDs within the two conditions
    sd_diff = mean_diff / d_diff,
    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
      (-2 * sd_novel * sd_familiar)
  ) %>%
  pull(ri) -> ri_empirical

@@

```{r, tabs1, include=TRUE}
# Save table of experiments for the meta-analysis of rotation
dat_meta %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = as.integer(sample_size),
    Females = as.integer(round(female_percent * sample_size)),
    Age = str_c(age_mean, "±", age_sd, sep = " "),
    Task = task,
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
  mutate(
    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
  ) -> tabs1

# Display the table
apa_table(
  tabs1,
  caption = "Experiments included in the main analysis",
  landscape = TRUE, font_size = "scriptsize"
)

# Save the table
dir.create(tables_dir, showWarnings = FALSE)
write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")
```

@@

# Display the table
apa_table(
  tabs2,
  caption = "Frequentist meta-analyses and meta-regression",
  font_size = "scriptsize",
  escape = FALSE,
  align = "llrrrrr",
)

# Save the table
write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))
```

@@

# Display the table
apa_table(
  tabs3,
  caption = "Jackknife (leave-one-out) analysis", font_size = "scriptsize",
  landscape = TRUE, escape = FALSE, align = "llrrrr"
)
```

@@

# Display the table
apa_table(
  tabs5,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE, align = "llrrrr"
)
```

@@

# Display the table
apa_table(
  tabs6,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
  align = "llrrrrrrr"
)
```

@@

# Display the table
apa_table(
  tabs7,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE, align = "llrrrrrrr"
)
```

@@

# Save the tables
write_csv(
  tabs_correction$meta,
  file = here(tables_dir, "tabs8_correction_meta.csv")
)
write_csv(
  tabs_correction$gender,
  file = here(tables_dir, "tabs9_correction_gender.csv")
)
```

```{r, tabs8, include=TRUE}
# Display the table
apa_table(
  tabs_correction$meta,
  caption = "Publication bias correction for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr"
)
```

```{r, tabs9, include=TRUE}
# Display the table
apa_table(
  tabs_correction$gender,
  caption = "Publication bias correction for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr",
)
```

>>>>

```{r, correlation}
# Compute empirical estimate of the correlation between dependent samples
dat_meta %>%
  mutate(
    # Get effect size from paired samples t-test, one sample t-test, or ANOVA
    d_diff = case_when(
      !is.na(d) ~ d,
      !is.na(d_z_t) ~ d_z_t,
      !is.na(d_z_f) ~ d_z_f,
      !is.na(d_z_diff) ~ d_z_diff
    ),
    # Compute empirical correlation
    # Based on the SD of the difference and the SDs within the two conditions
    sd_diff = mean_diff / d_diff,
    ri = (sd_diff^2 - sd_novel^2 - sd_familiar^2) /
      (-2 * sd_novel * sd_familiar)
  ) %>%
  pull(ri) -> ri_empirical

@@

```{r, tabs1, include=TRUE}
# Save table of experiments for the meta-analysis of rotation
dat_meta %>%
  mutate(
    age_mean = print_days_months(age_mean),
    age_sd = str_c(as.character(round(age_sd)), "d"),
  ) %>%
  transmute(
    Article = if_else(article == lag(article, default = ""), "", article),
    Experiment = group_long,
    `Sample size` = as.integer(sample_size),
    Females = as.integer(round(female_percent * sample_size)),
    `Age ($M$ ± $SD$)` = str_c(age_mean, "±", age_sd, sep = " "),
    Task = as.character(task),
    `Stimulus type` = str_to_sentence(stimuli_presentation),
    `Stimulus dimensions` = stimuli_dimensions
  ) %>%
  mutate(
    across(.fns = function(x) ifelse(is.na(x), "n/a", x))
  ) -> tabs1

# Save the table
dir.create(tables_dir, showWarnings = FALSE)
write_csv(tabs1, file = here(tables_dir, "tabs1_experiments.csv"), na = "n/a")

# Add footnotes
colnames(tabs1)[5] <- str_c(colnames(tabs1)[5], "\\textsuperscript{a}")
tabs1$Females[1] <- str_c(tabs1$Females[1], "\\textsuperscript{b}")
tabs1$Task[3] <- str_c(tabs1$Task[3], "\\textsuperscript{c}")

# Display the table
apa_table(
  tabs1,
  caption = "Experiments included in the main analysis",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = mean ± standard deviation, ",
    "\\textsuperscript{b} = not available, ",
    "\\textsuperscript{c} = violation of expectation."
  ),
  landscape = TRUE, font_size = "scriptsize", escape = FALSE
)
```

@@

# Save the table
write_csv(tabs2, file = here(tables_dir, "tabs2_frequentist.csv"))

# Add footnotes
colnames(tabs2)[4] <- str_c(colnames(tabs2)[4], "\\textsuperscript{a}")
colnames(tabs2)[7] <- str_c(colnames(tabs2)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs2,
  caption = "Frequentist meta-analyses and meta-regression",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize",
  escape = FALSE,
  align = "llrrrrr"
)
```

@@

# Add footnotes
colnames(tabs3)[6] <- str_c(colnames(tabs3)[6], "\\textsuperscript{a}")

# Display the table
apa_table(
  tabs3,
  caption = "Jackknife (leave-one-out) analysis", font_size = "scriptsize",
  note = "\\scriptsize\\textsuperscript{a} = intraclass correlation.",
  landscape = TRUE, escape = FALSE, align = "llrrrr"
)
```

@@

# Add footnotes
colnames(tabs5)[6] <- str_c(colnames(tabs5)[6], "\\textsuperscript{a}")
tabs5$` `[8] <- str_c(tabs5$` `[8], "\\textsuperscript{b}")
tabs5$` `[9] <- str_c(tabs5$` `[9], "\\textsuperscript{c}")
tabs5$` `[10] <- str_c(tabs5$` `[10], "\\textsuperscript{d}")
tabs5$` `[11] <- str_c(tabs5$` `[11], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs5,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = intraclass correlation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrr"
)
```

@@

# Add footnotes
tabs6$` `[8] <- str_c(tabs6$` `[8], "\\textsuperscript{a}")
tabs6$` `[9] <- str_c(tabs6$` `[9], "\\textsuperscript{b}")
tabs6$` `[10] <- str_c(tabs6$` `[10], "\\textsuperscript{c}")
tabs6$` `[11] <- str_c(tabs6$` `[11], "\\textsuperscript{d}")

# Display the table
apa_table(
  tabs6,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{b} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{c} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{d} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
  align = "llrrrrrrr"
)
```

@@

# Add footnotes
colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
tabs7$` `[1] <- str_c(tabs7$` `[1], "\\textsuperscript{b}")
tabs7$` `[2] <- str_c(tabs7$` `[2], "\\textsuperscript{c}")
tabs7$` `[3] <- str_c(tabs7$` `[3], "\\textsuperscript{d}")
tabs7$` `[4] <- str_c(tabs7$` `[4], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs7,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = intraclass correlation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrrrr"
)
```

@@

# Save the tables
tabs8 <- tabs_correction$meta
tabs9 <- tabs_correction$gender
write_csv(tabs8, file = here(tables_dir, "tabs8_correction_meta.csv"))
write_csv(tabs9, file = here(tables_dir, "tabs9_correction_gender.csv"))
```

```{r, tabs8, include=TRUE}
# Add footnotes
colnames(tabs8)[4] <- str_c(colnames(tabs8)[4], "\\textsuperscript{a}")
colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs8,
  caption = "Publication bias correction for the meta-analysis of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr"
)
```

```{r, tabs9, include=TRUE}
# Add footnotes
colnames(tabs9)[4] <- str_c(colnames(tabs9)[4], "\\textsuperscript{a}")
colnames(tabs9)[7] <- str_c(colnames(tabs9)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs9,
  caption = "Publication bias correction for the meta-analysis of gender differences",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr",
)
```
